Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-05 soundness.tex
+

\begin{assumption}
\label{assumption}
Iris defines two pieces of ghost state
\begin{enumerate}
\item  defines a predicate $\genheapinterp\store.\mathcal{R}$
  that ties a store~$\store.\mathcal{R}$ to this ghost state,
  and defines the points-to assertion $\ppointsto\rg\rv\qfrac\rpts$
  in terms of this ghost state.
  This is visible in the paper~\cite[\S6.3.2]{iris}
  and in Iris's \texttt{gen\_heap} library~\cite{genheap}.
  %
  We re-use this machinery without change,
  so we do not repeat these definitions.
  We mention the predicate $\genheapinterp\!$
  in our own invariant (Definition~\ref{def:invariant}),
  where it is applied to the \logical store~$\store$.
\item unlike the points-to relation obtained by direct interpretion of $\genheapinterp\store.\mathcal{R}$ using Iris, the existing \textsf{gen\_heap\_interp},
  does not directly helps introducing the ghost we define a new algebra (\textsf{gen\_mem\_UR}) for abstracting the nested maps due to different levels of masking in memory mappings and an interpretation for this algebra. 
\end{enumerate}
\end{assumption}

@@

\begin{definition}[Central Invariant]
\label{def:invariant}
The central invariant of our logic is, due to lack of need for augmenting the machine state, simply the state interpretation \cite[\S7.3]{iris} : 
\[
\centralinvariant\;\store \triangleq
\left\{
\def\arraystretch{1.2}
\begin{array}{l@{\quad\star\quad}l@{\quad}l}
  \genheapinterp\store &  \\
   \genmemheapinterp\store
\end{array}
\right.
\]
\end{definition}

As noted earlier (Assumption~\ref{assumption}), the predicate
$\genheapinterp\!$ and the points-to assertion for register mappings is inherited from Iris. What
this means, as far as we are concerned, is that the points-to assertion is
defined in a standard manner: $\genheapinterp\!$ is applied to the physical store~$\store$, as is usually the case~\cite[\S6.3.2]{iris}.
Likewise, we define nested interpretation $\genmemheapinterp\!$ in terms of $\genheapinterp\!$ to obtain physical memory points-to relation.

In fact, long story short, all assertions in our logic, i.e. points-to assertions for registers and memory, really about the logical store, which is in our case identical to the physical store, so that we can reason about the physical store.

>>>>

\begin{assumption}
\label{assumption}
Iris defines two pieces of ghost state
\begin{enumerate}
\item  defines a predicate $\textsf{to\_gen\_heap }\store.\mathcal{R}$
  that ties a store~$\store.\mathcal{R}$ to this ghost state,
  and defines the points-to assertion $\ppointsto\rg\rv\qfrac\rpts$
  in terms of this ghost state.
  This is visible in the paper~\cite[\S6.3.2]{iris}
  and in Iris's \texttt{gen\_heap} library~\cite{genheap}.
  %
  We re-use this machinery without change,
  so we do not repeat these definitions.
  We mention the predicate $\genheapinterp\!$
  in our own invariant (Definition~\ref{def:invariant}),
  where it is applied to the \logical store~$\store$.
\item unlike the register points-to relation obtained by direct interpretion of $\textsf{to\_gen\_heap }\store.\mathcal{R}$ using Iris, the existing \textsf{gen\_heap\_heap},
  does not directly helps introducing the ghost we define a new algebra (\textsf{gen\_mem\_UR}) for abstracting the nested maps due to different levels of masking in memory mappings and an interpretation for this algebra. 
\end{enumerate}
\end{assumption}

@@

\begin{definition}[Central Invariant]
\label{def:invariant}
The central invariant of our logic is, due to lack of need for augmenting the machine state, simply the state interpretation \cite[\S7.3]{iris} : 
\[
\centralinvariant\;\store \triangleq
\left\{
\def\arraystretch{1.2}
\begin{array}{l@{\quad\star\quad}l@{\quad}l}
  \textsf{to\_gen\_heap} \;\store.\mathcal{R} &  \\
   \textsf{to\_gen\_mem} \; \store.\mathcal{M}
\end{array}
\right.
\]
\end{definition}

Now, we have well-enough definition for giving an outline for the proof of \TirNameStyle{WriteToRegFromVirtMem}.
\todo[inline,color=red]{ISMAIL give the outlin}
